Lens Modeling in Spacewarps

### 2013-07-24 text/ms.tex
some text

\title{Something about Lens Models}

@@

\begin{abstract}
This is an abstract.
\end{abstract}

@@

See Figure \ref{fig:ASW0000kad}.

@@

@@

Can replace comoving distances $D$ with angular-diameter distances
$d$, as follows
\begin{equation}
\begin{aligned}
D_L    &= (1+z_L) d_{OL}
D_{LS} &= \frac{1+z_S}{1+z_L} d_{LS}
D_S    &= (1+z_L) d_{OS}
\end{aligned}
\end{equation}
and
\begin{equation}
(x,y) = d_{OL} (\theta_x,\theta_y)
\end{equation}

@@

\begin{figure}
\includegraphics[width=.3\hsize]{ASW0000kadC_kappa.png}
\includegraphics[width=.3\hsize]{ASW0000kadC_arriv.png}
\includegraphics[width=.3\hsize]{ASW0000kadC_menc.png}
\caption{This is a figure.\label{fig:ASW0000kad}}
\end{figure}

>>>>

\title{Lens Modeling in Spacewarps}

@@

\begin{abstract}
In Spacewarps, volunteers are invited to search sky surveys for lens
candidates.  Here we report on a system that allows experienced
volunteers to model lens candidates.  A sample of 29 simulated lenses
were modelled, each multiple times.  The quality of the models was
then examined in two ways.  First, the image parities and time
orderings: these were identified correctly in most cases, but not
always.  Second, the mean convergence (equivalent to the enclosed
mass): this was constrained consistently well in the image region.
The performance of professionals and experienced volunteers was
comparable.
\end{abstract}

@@

@@

Example Figure \ref{fig:ASW0000ar2}.

@@

Can replace comoving distances $D$ with angular-diameter distances
$d$,
\begin{equation}
(x,y) = d_L (\theta_x,\theta_y)
\end{equation}
and so on.
\begin{equation}
\begin{aligned}
D_S &= (1+z_S) \, d_S \\
D_{LS} &= \frac{1+z_S}{1+z_L} \, d_{LS} \\
D_L &= (1+z_L) \, d_L
\end{aligned}
\end{equation}
Angular-diameter distances are always smaller than comoving distances.

@@

\begin{figure}
\includegraphics[width=.32\hsize]{ASW0000ar2Q_kappa.png}
\includegraphics[width=.32\hsize]{ASW0000ar2Q_arriv.png} \\
\includegraphics[width=.32\hsize]{ASW0000ar2_kappa.png}
\includegraphics[width=.32\hsize]{ASW0000ar2_arriv.png}
\includegraphics[width=.32\hsize]{ASW0000ar2_menc.png}
\caption{A simple two-image lensed quasar.  The minimum and saddle are
  identified correctly.  The mean model shows two spurious images, but
  the mean convergence in the region of images is good.
\label{fig:ASW0000ar2}}
\end{figure}
